\\textbf{\\textsc{Supplementary Material} \\linebreak \\linebreak Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution \\linebreak \\linebreak Methods to create \\textsl{the scatterblob} figure}

### 2022-12-14 R/Supp_Info_1.Rmd
Renames `scatterblob.Rmd` to `Supp_Info_1.Rmd`

The collaborative [google spread sheet](https://docs.google.com/spreadsheets/d/1zCRgctjfjE2xZN9MkqfFh222K6bvVvA3gT0UdkL_CS8/edit#gid=0), features a first column listing the ways to use GitHub that were addressed in the manuscript (`r paste0(uses[1:12], collapse = "; " )`).

@@

if (plot_format == "pdf") {
  pdf(file = here(outpath, "scatterblob_0.pdf"),
      width = 8.25,
      height = 6,
      bg = "white")  
}
if (plot_format == "svg") {
  svg(filename = here(outpath, "scatterblob_0.svg"),
      width = 8.25,
      height = 6,
      bg = "white")  
}
if (plot_format == "png") {
  png(file = here(outpath, "scatterblob_0.png"),
      width = 8.25,
      height = 6,
      units = "in",
      res = 300,
      bg = "white")  
}
par(xpd = NA,
    mai = c(1.02, 1, 0.82, 4),
    bty="n")
###############################################################
# create the plot background
###############################################################
plot(x = c(0.5, 5.5),
     y = c(1.75, 10.75),
     xlab = "",
     ylab = "",
     col = "white",
     # "hide" the tick labels so we can put some words instead of numbers:
     col.axis = "white",
     tck = 0.02)
title(ylab="Technical difficulty", line=4, cex.lab=1)
title(xlab="Degree of collaboration", line= 3.5, cex.lab=1)
###############################################################
# add tick labels
###############################################################
text(x = 1:5,
     y = c(1, rep(1.05, 4)),
     cex = 0.7,
     labels = c("Personal",
                "Lab \nMembers",
                "Other \nLabs",
                "EEB \nCommunity",
                "All \nUsers"))
text(x = c(1, 3, 5),
     y = 0.5,
     labels = c("Low", "Medium", "High"))
# Technical difficulty levels from https://www.londonschool.com/level-scale/
text(x = 0.2,
     y = c(2, 4, 6, 8, 10),
     cex = 0.7,
     adj = 1,
     labels = c("Elementary",
                "Low \nIntermediate",
                "Intermediate",
                "Pre \nAdvanced",
                "Very \nAdvanced"))
###############################################################
# plot scatter blobs
###############################################################
for (i in seq(nrow(my_data))) {
  X0 <- my_data$x1[i]
  X1 <- my_data$x2[i]
  Y <- my_data$y_real[i]
  if (X0 == X1) {
    X0 <- X0 - 0.01
    X1 <- X1 + 0.01
   }
  segments(x0 = X0,
           x1 = X1,
           y0 = Y,
           col = my_colors[i],
           lwd = 13)
}
###############################################################
# add github uses text
###############################################################
text(x = 5.5,
    y = my_data$y_real,
    labels = my_data$`Ways to use GitHub`,
    adj = 0,
    col = my_colors)
dev.off()
```

@@

if (plot_format == "pdf") {
  pdf(file = here(outpath, paste0(plot_name, ".pdf")),
      width = 8.25,
      height = 6,
      bg = "white")  
}
if (plot_format == "svg") {
  svg(filename = here(outpath, paste0(plot_name, ".svg")),
      width = 8.25,
      height = 6,
      bg = "white")  
}
if (plot_format == "png") {
  png(file = here(outpath, paste0(plot_name, ".png")),
      width = 8.25,
      height = 6,
      units = "in",
      res = 300,
      bg = "white")  
}
par(xpd = NA,
    mai = c(1.02, 1, 0.82, 4),
    bty="n")
###############################################################
# create the plot background
###############################################################
plot(x = c(0.5, 5.5),
     y = c(0.4, 14),
     xlab = "",
     ylab = "",
     col = "white",
     # "hide" the tick labels so we can put some words instead of numbers:
     col.axis = "white",
     tck = 0.02)

@@

![Degree of collaboration VS technical difficulty (sequential)](../content/images/scatterblob_1-viridis-turbo.png)

>>>>

The collaborative [google spread sheet](https://docs.google.com/spreadsheets/d/1zCRgctjfjE2xZN9MkqfFh222K6bvVvA3gT0UdkL_CS8/edit#gid=0), features a first column listing the ways to use GitHub that were addressed in the manuscript (`r paste0(uses[1:13], collapse = "; " )`).

@@

if (plot_format == "pdf") {
  pdf(file = here(outpath, "scatterblob_0.pdf"),
      width = 8.25,
      height = 6,
      bg = "white")  
}
if (plot_format == "svg") {
  svg(filename = here(outpath, "scatterblob_0.svg"),
      width = 8.25,
      height = 6,
      bg = "white")  
}
if (plot_format == "png") {
  png(file = here(outpath, "scatterblob_0.png"),
      width = 8.25,
      height = 6,
      units = "in",
      res = 300,
      bg = "white")  
}
par(xpd = NA,
    mai = c(1.02, 1, 0.82, 4),
    bty="n")
###############################################################
# create the plot background
###############################################################
plot(x = c(0.5, 5.5),
     y = c(1.75, 11.5),
     xlab = "",
     ylab = "",
     col = "white",
     # "hide" the tick labels so we can put some words instead of numbers:
     col.axis = "white",
     tck = 0.02)
title(ylab="Technical difficulty", line = 4, cex.lab = 1)
title(xlab="Degree of collaboration", line = 3.5, cex.lab = 1)
###############################################################
# add tick labels
###############################################################
text(x = 1:5,
     y = c(1, rep(1.05, 4)),
     cex = 0.7,
     labels = c("Personal",
                "Lab \nMembers",
                "Other \nLabs",
                "EEB \nCommunity",
                "All \nUsers"))
text(x = c(1, 3, 5),
     y = 0.5,
     labels = c("Low", "Medium", "High"))
# Technical difficulty levels from https://www.londonschool.com/level-scale/
text(x = 0.2,
     y = c(2, 4, 6, 8, 10),
     cex = 0.7,
     adj = 1,
     labels = c("Elementary",
                "Low \nIntermediate",
                "Intermediate",
                "Pre \nAdvanced",
                "Very \nAdvanced"))
###############################################################
# plot scatter blobs
###############################################################
for (i in seq(nrow(my_data))) {
  X0 <- my_data$x1[i]
  X1 <- my_data$x2[i]
  Y <- my_data$y_real[i]
  if (X0 == X1) {
    X0 <- X0 - 0.01
    X1 <- X1 + 0.01
   }
  segments(x0 = X0,
           x1 = X1,
           y0 = Y,
           col = my_colors[i],
           lwd = 13)
}
###############################################################
# add github uses text
###############################################################
text(x = 5.5,
    y = my_data$y_real,
    labels = my_data$`Ways to use GitHub`,
    adj = 0,
    col = my_colors)
dev.off()
```

@@

if (plot_format == "pdf") {
  pdf(file = here(outpath, paste0(plot_name, ".pdf")),
      width = 8.25,
      height = 6,
      bg = "white")  
}
if (plot_format == "svg") {
  svg(filename = here(outpath, paste0(plot_name, ".svg")),
      width = 8.25,
      height = 6,
      bg = "white")  
}
if (plot_format == "png") {
  png(file = here(outpath, paste0(plot_name, ".png")),
      width = 8.25,
      height = 6,
      units = "in",
      res = 300,
      bg = "white")  
}
par(xpd = NA,
    mai = c(1.02, 1, 0.82, 4),
    bty="n")
###############################################################
# create the plot background
###############################################################
plot(x = c(0.5, 5.5),
     y = c(0.5, 13.5),
     xlab = "",
     ylab = "",
     col = "white",
     # "hide" the tick labels so we can put some words instead of numbers:
     col.axis = "white",
     tck = 0.02)

@@

![Degree of collaboration _versus_ technical difficulty (sequential)](../content/images/scatterblob_1-viridis-turbo.png)
